\section{Vocabulary}

\paragraph{Dataset used}
In order to link the concepts in the user profile to known uniquely identifiable concepts in the Linked Open Data
cloud\footnote{http://linkeddata.org}, we used vocabularies from the \textit{Freebase} service.

Freebase is a service offering a large (over 10 million topics) amount of semantically linked data on various topics.

The data available on Freebase is divided into \textit{topics}, types and properties. \textit{Topics} correspond to data
freely available, similar to \textit{Wikipedia}, describing physical entities, artistic creations, abstract concepts
etc. In comparison to \textit{Wikipedia}, all of the data on \textit{Freebase} is semantically structured,
allowing users to edit, add and remove data. As mentioned, the \textit{Freebase} project is a part of Linked Open Data.

\textit{Types} refer to different aspects of the same topic (\eg \textit{Bob Dylan} is a song writer,
singer and a film actor which all represent different types). All types have properties referring those
types to the topics (such as songs that Bob Dylan has written).

All topics and types have IDs expandable into URIs pointing to their location in the \textit{Freebase} dataset
(such as \textit{/en/tina\_fey}\footnote{www.freebase.com/view/en/tina\_fey} for actress \textit{Tina Fey}
or \textit{/medicine/disease}\footnote{www.freebase.com/view/medicine/disease} for the type \textit{Disease}).
By referring to those IDs a user is able to search Freebase for more linked data regarding the interesting topic and type.

From the whole wealth of data, we have focused only on the data related to the media, such as TV Actors, Movies, Movie
actors and TV Programmes as well as Bands and Singers' names.

\paragraph{Usage in the research}
We have decided to use the \textit{Freebase} dataset in order to be able to uniquely identify mentions of different NEs
within the available UAD. This approach is beneficial for use with recommender systems (such as the recommender
in the \textit{NoTube} profject), enabling them to immediately use the wealth of relational semantic data available
in the \textit{Linked Open Data cloud} for expanding their recommendations to related concepts.
