\section{Extracting user profile from YouTube}
\subsection{YouTube counting strategies}

\begin{itemize}
\item{Tags aggregation across various video sets:
\begin{itemize}
  \item{User's likes and favourites}
  \item{User's subscriptions (two-level aggregation there)}
  \item{User's history}
  \item{User's uploads}
\end{itemize}
}

\item{Similar aggregation for other entities found in videos
\begin{itemize}
  \item{Puropose of the video -- we could invent a dictionary of video purposes
  (eg. advertisements, lectures, speeches, movie fragments, family videos) and
  relate them to the videos.}
  \item{Keywords from comments -- after the aggregation and rejecting of stop
  words, this might prove userful.}
  \item{Language -- could be estimated by analysis of language of
  comments and description, location of the publisher and commenters.}
  \item{Duration -- users might prefer shorter clips. This might happen only for
  certain types of videos (lectures, advertisements).}
  \item{Freshness -- users might prefer videos uploaded more recently. This
  might be useful for example to identify "sneak peeks" for TV shows.}
  \item{Controversiality -- likes/dislikes ratio, amount of favourites per
  views.}
  \item{Second order effects -- facts determined for a video might be applicable
  also for a clip it is a response to.}
\end{itemize}
}

\item{Relating videos and channels to entities from other linked data services
\begin{itemize}
  \item{People: music artists, actors, directors, politicians, TV presenters,
  other public figures}
  \item{Places: cities, countries}
  \item{Existing works: TV programmes, movies, music tracks}
  \item{Others: musical, political, traditional and commercial events, brands}
\end{itemize}
}
\end{itemize}

\subsection{Counting YouTube tags and categories}
The most obvious way to get profiling information is through the use of
tags. However, tags of a single video clip can be either too numerous, making many
of them irrelevant, too sparse, nonexistent and occasionally just wrong. To avoid
that problem, we aggregate the tags across sets of video clips related to the
profiled user (favourites, subscriptions, uploads). Similar aggregation was
performed for the videos' categories. Below is a comparison of results of counting
tags (chosen by the user) and categories (picked from a small predefined set).


\begin{table}[ht]
\begin{minipage}[b]{0.5\linewidth}\centering

\begin{tabular}{| l | l |}
Category & \# \\ \hline
News & 8 \\
Music & 5 \\
Education & 3 \\
Comedy & 2 \\
\end{tabular}

\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.5\linewidth}
\centering

\begin{tabular}{| l | l |}
Tag & \# \\ \hline
sonik & 5 \\
bogusław & 5 \\
trzech & 5 \\
kupli & 5 \\
wybory & 4 \\
kraków & 4 \\
polska & 4 \\
\end{tabular}

\end{minipage}

\caption{Most popular tags and categories from account of Bogusław Sonik -- a
polish politician. The word ''wybory'' stands for ''election'' in polish, and
\emph{Trzech kumpli} is a title of a controversial political documentary.}
\end{table}


\begin{table}
\begin{minipage}[b]{0.5\linewidth}\centering

\begin{tabular}{| l | l |}
Category & \# \\ \hline
Music & 53 \\
Comedy & 20 \\
Entertainment & 8 \\
Games & 4 \\
People & 3 \\
Travel & 3 \\
News & 2 \\
\end{tabular}

\end{minipage}
\hspace{0.5cm}
\begin{minipage}[b]{0.5\linewidth}
\centering

\begin{tabular}{| l | l |}
Tag & \# \\ \hline
metal & 17 \\
music & 11 \\
rock & 11 \\
video & 7 \\
the & 7 \\
black & 7 \\
of & 7 \\
\end{tabular}

\end{minipage}

\caption{Most popular tags and categories from anonymous user -- apparently a
heavy metal music fan}
\end{table}

We can see that category count, even though providing general overview of
person's interests (and the ways she uses youtube), cannot be used to find
specific interests. In other words: we can say that a person is more keen to
favourite music videos or comedy videos after looking at his categories, but in
order to say what kind of music the person prefers, we need more specific
information gathered from (e.g.) tags.

\subsection{How to handle duplicates}

When combining tags collected from various sets of videos, a question should be
asked what preference -- if any -- should be given to tags appearing in more
then one of them. Let's analyze some examples. The letters $f$, $s$ and $u$ mean number
of videos in accordingly: favourites, subscriptions and uploads. The
combinations of letters indicate numbers of tags repeating in these sets.

\begin{tabular}{| l | l | l | l | l | l | l | l |}
user & $f$ & $s$ & $u$ & $fs$ & $fu$ & $su$ & $fsu$ \\ \hline
politician & 219 & 32321 & 357 & 116 & 59 & 156 & 34 \\
metal music fan & 1103 & 7570 & 73 & 533 & 27 & 44 & 26 \\
one of authors & 687 & 5553 & 10 & 199 & 2 & 2 & 1 \\
\end{tabular}

The tags that appeared in all three sets are:
\begin{itemize}
  \item{politician: \emph{wybory, europarlament, czerwca, europa, europejska,
  parlament, 18, unia, europejski, kraków, w, 7, pe, 2009, bogusław, po,
  bezpieczeństwo}}
  \item{metal music fan: \emph{head, death, pantera, for, in, nosturi, the, live, cover, metal}}
  \item{one of authors: \emph{film}}
\end{itemize}

As expected, the repeating tags give much more precise view of person's
interests. Unfortunately, the tags get muted when a user is not active in one of
those areas (e.g. does not upload movies very frequently).

\subsection{The double nestedness problem}
Gathering tags across user's favourites or uploads let us treat the whole video
set as a single document, giving each tag equal weight in the counting process.
Taking a similar approach for subscriptions (e.g. giving equal weight to each
tag of each video of every subscription) leads to some unwanted effects.

Suppose a user subscribes to two channels. One represents the british royal
family (133 uploads), the other one: Apple Inc., an american computer company
(19 uploads). The tags referring to new hardware releases would get flooded with
tags regarding british-specific content. In effect, the user's profile would
depend on third parties' youtube activity which is doubtful to be of any
importance to her.

In order to counteract this effect a number of techniques can be used. One of
them is giving each subscription a weight, based on the number of videos or
total number of tags.

\subsection{Identifying entities in youtube streams}
The user profile information would largely benefit from including data aligned
to existing Linked Data sources. An attempt to run this task trivially for
several types of entities (actors, networks) have been performed. The approach
was to identify actors names by a simple text search in videos' titles and
descriptions. Below are sample results (note that descriptions are not shown):

\begin{verbatim}
Rowan Atkinson LIVE: 02 - Fatal Beatings          , Rowan Atkinson
Yes We Can - Barack Obama Music Video             , Scarlett Johansson
Compay Segundo - Chan Chan                        , Compay Segundo
Drivin' Me Wild - Common Ft Lily Allen [OFFICIAL] , Lily Allen
PT 4 - BRITNEY SPEARS 2006 INTERVIEW BEARS ALL    , Britney Spears
16-Lovestoned Live Futuresex/Loveshow             , Justin Timberlake
15- Cry Me A River Live Futuresex/Loveshow        , Justin Timberlake
Jennifer Lopez - Ain't It Funny                   , Jennifer Lopez
Christina Aguilera - Save Me From Myself [Official, Christina Aguilera
Nancy Sinatra Bang Bang                           , Nancy Sinatra
Eddie Vedder - Hard Sun (Official Video)          , Eddie Vedder
\end{verbatim}

The approach is not ideal. However, above certain threshold of repeats, an
assumption that a user likes a given actor becomes more probable.

